The College Application Problem

### 2022-06-09 slides_25min/slides.tex
25min slides and script
move paper to own folder, make file

4개의 알고리즘 제시:
\begin{itemize}
\item 선형 완화 문제와 해당 \textbf{branch-and-bound} 해법. 일반적인 INLP 문제에 대해 자주 쓰이는 방법이다.

@@

\begin{frame}{\ifen Branch-and-bound algorithm: LP relaxation\else 분지한계법: 선형 완화 문제\fi}
\ifen
Our branch-and-bound framework is based on the following LP relaxation for Ellis's problem. 
\else
다음 선형 완화 문제 바탕으로 엘리스의 문제를 위한 분지한계법을 구성할 수 있다. 
\fi
\begin{problem}[\ifen LP relaxation for Ellis's problem\else 엘리스의 문제를 위한 선형 완화 문제\fi] %\label{LPrelaxation}
\vspace{-1em}
\begin{align*}
\begin{split}
\text{maximize}\quad &  v_{\mathrm{LP}}(x) = \sum_{j=1}^m  f_j t_j x_j \\
\text{subject to}\quad & \sum_{j=1}^m g_j x_j \leq H, ~~ x \in [0, 1]^m
\end{split}
\end{align*}
\end{problem}
\ifen
This is a continuous knapsack problem, easy to solve (Dantzig 1957; Balas and Zemel 1980). 
\else
연속 배낭 문제라고 불리며 쉽게 풀 수 있다 (Dantzig 1957; Balas와 Zemel 1980). 
\fi
\end{frame}

\begin{frame}{\ifen Branch-and-bound algorithm: Possible improvements\else 분지한계법: 개선 방향\fi}
\ifen
We \textbf{tighten the LP bound} by recycling the variable-elimination technique from the proof of the nestedness theorem.

A straightforward implementation is OK on small instances ($m \leq 35$), but leaves \textbf{considerable room for improvement} using better node-selection heuristics.

@@

In the associated Julia package, we provide \textbf{modular containers for subproblems and their LP relaxations} that can interface with a more sophisticated branch-and-bound solver.
\else
포함 사슬 관계의 증명 과정에서 도출한 변수 소거법은 재활용해서 위에 \textbf{상한을 더 타이트하게} 조정한다.

이 기반으로 만든 간단한 알고리즘은 작은 ($m \leq 35$) 인스턴스에 괜찮지만 분지 마디를 선택하는 휴리스틱으로 \textbf{개선할 여지}가 보인다.

Julia 코드 패키지에서 \textbf{부문제와 선형 완화 문제를 위한 modular한 데이터 구현을} 제시하며, 이를 더 세련된 INLP 솔버에 어렵지 않게 연결할 수 있다.
\fi
\end{frame}

@@

\begin{frame}{\ifen Valuation-based dynamic program: Recursion relation \else 포트폴리오 가치 기반 동적 계획: 재귀 관계 \fi}
\ifen 
Let $G[j, v]$ denote the application cost of the least expensive portfolio that uses only schools $\{ 1, \dots, j\}$ and has (rounded) valuation at least $v$. We argue that
\else
$\{ 1, \dots, j\}$에 속한 학교만 사용하면 (내림한) 가치가 최소한 $v$의 포트폴리오 중 지원 비용이 최소한 포트폴리오의 지출액을 $G[j, v]$라고 하자. 이때 다음 재귀 관계가 성립한다고 주장한다.
\fi
\begin{align*}
G[j, v] &=
\begin{cases}
\infty, \quad & t_j < v \\
\min\bigl\{G[j-1, v], g_j + G[j-1, v - \Delta_j(v)] \bigr\}, \quad & t_j \geq v 
%\begin{cases}
%\min\bigl\{G[j-1, v], g_j + G[j-1, v - \Delta] \bigr\}, \quad &f_j < 1 \\
%\min\bigl\{G[j-1, v], g_j \bigr\}, \quad &f_j = 1 \text{ and } f_j t_j \geq v\\
%G[j-1, v], \quad &f_j = 1 \text{ and } f_j t_j < v
\end{cases}\\
\text{where}\qquad
\Delta_j (v) &= 
\begin{cases}
r\left[\frac{f_j}{1 - f_j} (t_j - v)\right], \quad & f_j < 1\\
\infty, &f_j = 1\ifen.\fi
\end{cases} \label{deltajvdef}
\end{align*}

@@

Recipe for an experimental instance with $m$ schools:
\begin{itemize}
\item Each $t_j$ drawn from an exponential distribution.
\item $f_j$ chosen to correlate inversely with $1/ t_j$ (creates reach/safety schools).
\item Alma's problem: $h = \lfloor m/2 \rfloor$.
\item Ellis's problem: $g_j$ small integers, $H = \lfloor \frac{1}{2} \sum g_j\rfloor$.
\end{itemize}

@@

각 칸에서 50개의 시장을 생성하고 최적해를 3번 계산한 것 중에 최소 시간을 기록. 표에서 나타나는 값은 평균 (표준편차) 시간이며 단위는 ms.
\fi
\begin{center}
\scalebox{0.92}{ %
\begin{tabular}{r|r@{~}r|r@{~}r}
\ifen 
 \textbf{\begin{tabular}[r]{@{}r@{}}\\$m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Greedy alg.\\with list\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Greedy alg.\\with heap\end{tabular}}}\\ \hline
 \else
 \textbf{\begin{tabular}[r]{@{}r@{}}\\$m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}탐욕 알고리즘\\(목록 구현)\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}탐욕 알고리즘\\(힙 구현)\end{tabular}}}\\ \hline
 \fi
    16 &           0.00 &        (0.00) &           0.01 &        (0.00) \\
    64 &           0.03 &        (0.00) &           0.08 &        (0.02) \\
   256 &           0.15 &        (0.01) &           0.97 &        (0.22) \\
  1024 &           2.31 &        (0.05) &          14.44 &        (1.66) \\
  4096 &          37.85 &        (0.61) &         245.74 &       (17.33) \\
 16384 &         585.75 &        (2.11) &        4728.59 &      (552.25)
\end{tabular}
}
\end{center}
\ifen 
$\argmax$ operation at each iteration made heap an appealing data structure, but because \emph{every} key is updated, the savings aren't worth the cost.
\else 
반복 단계마다 $\argmax$ 연산이 필요하므로 힙 구현에는 매력이 있지만, 그의 모든 원소를 수정해야 하므로 만회하지 않는다.
\fi

>>>>

4개의 알고리즘 제시:
\begin{itemize}
\item 선형 완화 문제와 해당 \textbf{분지한계} (branch-and-bound) 해법. 일반적인 INLP 문제에 대해 자주 쓰이는 방법이다.

@@

\begin{frame}{\ifen Branch-and-bound algorithm: LP relaxation\else 분지한계법: 선형 완화 문제\fi}
\ifen
Our branch-and-bound framework is based on the following LP relaxation for Ellis's problem. 
\else
다음 선형 완화 문제 바탕으로 엘리스의 문제를 위한 분지한계법을 구성할 수 있다. 
\fi
\begin{problem}[\ifen LP relaxation for Ellis's problem\else 엘리스의 문제를 위한 선형 완화 문제\fi]\label{LPrelaxation}
\vspace{-2em}
\begin{align*}
\begin{split}
\text{maximize}\quad &  v_{\mathrm{LP}}(x) = \sum_{j=1}^m  f_j t_j x_j \\
\text{subject to}\quad & \sum_{j=1}^m g_j x_j \leq H, ~~ x \in [0, 1]^m
\end{split}
\end{align*}
\end{problem}
\ifen
We \textbf{tighten the LP bound} by recycling the variable-elimination technique from the proof of the nestedness theorem.

Problem \ref{LPrelaxation} is a continuous knapsack problem, easy to solve (Dantzig 1957; Balas and Zemel 1980). 
\else
포함 사슬 관계의 증명 과정에서 도출한 변수 소거법은 재활용해서 위에 \textbf{상한을 더 타이트하게} 조정한다.

문제 \ref{LPrelaxation}은 연속 배낭 문제로서 쉽게 풀 수 있다 (Dantzig 1957; Balas와 Zemel 1980). 
\fi
\end{frame}

\begin{frame}{\ifen Branch-and-bound algorithm: Possible improvements\else 분지한계법: 개선 방향\fi}
\ifen
A straightforward implementation is OK on small instances ($m \leq 35$), but leaves \textbf{considerable room for improvement} using better node-selection heuristics.

@@

In the associated Julia package, we provide \textbf{modular containers for subproblems and their LP relaxations} that can interface with a more sophisticated branch-and-bound solver.

A branch-and-bound algorithm may be necessary to handle more advanced constraint structures.
\else
이 기반으로 만든 간단한 알고리즘은 작은 ($m \leq 35$) 인스턴스에 괜찮지만 분지 마디를 선택하는 휴리스틱으로 \textbf{개선할 여지가} 보인다.

Julia 코드 패키지에서 \textbf{부문제와 선형 완화 문제를 위한 modular한 데이터 구현을} 제시하며, 이를 더 세련된 INLP 솔버에 어렵지 않게 연결할 수 있다.

나중에 더 복합한 제약 조건을 도입하는 데에 분지한계법 알고리즘이 필요할 수 있으므로 유리하다.
\fi
\end{frame}

@@

\begin{frame}{\ifen Valuation-based dynamic program: Recursion relation \else 포트폴리오 가치 기반 동적 계획: 재귀 관계 \fi}
\ifen 
Let $G[j, v]$ denote the application cost of the least expensive portfolio that uses only schools $\{ 1, \dots, j\}$ and has (rounded) valuation at least $v$. We argue that
\else
$\{ 1, \dots, j\}$에 속한 학교만 사용하면 (내림한) 가치가 최소한 $v$의 포트폴리오 중 지원 비용이 최소한 포트폴리오의 지출액을 $G[j, v]$라고 하자. 이때 다음 재귀 관계가 성립한다고 주장한다.
\fi
\begin{align*}
G[j, v] &=
\begin{cases}
\infty, \quad & t_j < v \\
\min\bigl\{G[j-1, v], g_j + G[j-1, v - \Delta_j(v)] \bigr\}, \quad & t_j \geq v 
%\begin{cases}
%\min\bigl\{G[j-1, v], g_j + G[j-1, v - \Delta] \bigr\}, \quad &f_j < 1 \\
%\min\bigl\{G[j-1, v], g_j \bigr\}, \quad &f_j = 1 \text{ and } f_j t_j \geq v\\
%G[j-1, v], \quad &f_j = 1 \text{ and } f_j t_j < v
\end{cases}\\
\text{where}\quad
\Delta_j (v) &= 
\begin{cases}
r\left[\frac{f_j}{1 - f_j} (t_j - v)\right], \quad & f_j < 1\\
\infty, &f_j = 1\ifen.\fi
\end{cases} \label{deltajvdef}
\end{align*}

@@

Recipe for an experimental instance with $m$ schools:
\begin{itemize}
\item Each $t_j$ drawn from an exponential distribution.
\item $f_j$ chosen to correlate with $1/ t_j$ (creates reach/safety schools).
\item Alma's problem: $h = \lfloor m/2 \rfloor$.
\item Ellis's problem: $g_j$ small integers, $H = \lfloor \frac{1}{2} \sum g_j\rfloor$.
\end{itemize}

@@

\looseness=-1
각 칸에서 50개의 시장을 생성하고 최적해를 3번 계산한 것 중에 최소 시간을 기록. 표에서 나타나는 값은 평균 (표준편차) 시간이며 단위는 ms.
\fi
\begin{center}
\scalebox{0.92}{ %
\begin{tabular}{r|r@{~}r|r@{~}r}
\ifen 
 \textbf{\begin{tabular}[r]{@{}r@{}}\\$m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Greedy alg.\\with list\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Greedy alg.\\with heap\end{tabular}}}\\ \hline
 \else
 \textbf{\begin{tabular}[r]{@{}r@{}}\\$m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}탐욕 알고리즘\\(목록 구현)\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}탐욕 알고리즘\\(힙 구현)\end{tabular}}}\\ \hline
 \fi
    16 &           0.00 &        (0.00) &           0.01 &        (0.00) \\
    64 &           0.03 &        (0.00) &           0.08 &        (0.02) \\
   256 &           0.15 &        (0.01) &           0.97 &        (0.22) \\
  1024 &           2.31 &        (0.05) &          14.44 &        (1.66) \\
  4096 &          37.85 &        (0.61) &         245.74 &       (17.33) \\
 16384 &         585.75 &        (2.11) &        4728.59 &      (552.25)
\end{tabular}
}
\end{center}
\ifen 
$\argmax$ operation at each iteration made heap an appealing data structure, but because \emph{every} key is updated, the savings aren't worth the cost.
\else 
반복 단계마다 $\argmax$ 연산이 필요하므로 힙 구현에는 매력이 있지만, 그의 모든 원소를 수정해야 하므로 만회하지 않는다.
\fi
